\documentclass[10pt]{article}
    \usepackage[english]{babel}
    \input{config/minimal-resume-config}
\begin{document}

\begin{center}
	% Personal
	% -----------------------------------------------------
	{\fontsize{\sizeone}{\sizeone}\fontspec[Path = fonts/,LetterSpace=15]{Montserrat-Regular} ROBERT PAUL}
	\\
	\vspace{2mm}
	{\fontsize{1em}{1em}\fontspec[Path = fonts/]{Montserrat-Light} mail@robertpaul.dev -- (831) 235-8681 -- San Francisco Bay Area}
\end{center}
% Chapter: Work Experience
% ------------------------

\chap{EXPERIENCE}{ \\
	\job
	{Dropbox}
	{Remote}
	{Software Engineer}
	{Jul 2024 - Present}
	{
		\begin{newitemize}
			\item {Assisted with planning, implementation, and rollout of a silent automatic migration to File Provider, handling two sync engines running concurrently without additional storage overhead. Currently rolled out to 100,000 external users.}
			\item {Implemented backend for handling automatic sync engine migrations to File Provider, allowing us to test initial automatic migrations on 10,000 external users.}
			\item {Performed major overhaul of low-level error handling for the macOS File Provider API, resulting in the diagnosis and resolution of several longstanding bugs.}
		\end{newitemize}
	}
	\subjob
	{Software Engineer Intern}
	{May 2023 - Aug 2023}
	{
	    \begin{newitemize}
			\item {Refactored an existing sync performance testing tool to run on developer machines in anticipation of deprecation of existing platform.}
			\item {Modified tool to benchmark competitor sync engines to direct engineering efforts around sync speed.}
		\end{newitemize}
	}
	\subjob
	{Launch Software Engineer Intern}
	{May 2022 - Aug 2022}
	{
	    \begin{newitemize}
			\item {Refactored existing codebase for migrating users from Google Drive to Dropbox to allow expansion for additional sync providers.}
			\item {Implemented first additional sync provider, providing OneDrive to Dropbox imports for users.}
		\end{newitemize}
	}
	\jobheader
	{Chico State IT Support Services}
	{Chico, CA}

	\jobtitle
	{Tier 2 Technician}
	{Jul 2022 - Jun 2024}

	\jobtitle
	{Service Desk Support Technician}
	{Jan 2022 - Jun 2022}

	\jobtitle
	{Computer Lab Assistant}
	{Aug 2021 - Dec 2021}
}
% Chapter: Education
% ------------------

\chap{EDUCATION}{ \\
	\school
	{California State University, Chico}
	{Aug 2020 - May 2024}
	{B.S. Computer Science}
	{Chico, CA}{}
}
% Chapter: Projects
% ------------------------

\chap{PROJECTS}{ \\
	\project
	{Chord of Calling}
	{Rust (axum)}
	{}
	{Webapp for organizing drafts for Magic: the Gathering, currently in development. Planned testing early 2026.\\}
	\project
	{Modron}
	{Python, MongoDB (Motor), Discord.Py}
	{github.com/rp50/Modron}
	{A Discord bot designed for planning sessions and tracking players and their characters in a West-Marches D\&D game.\\}
}
% Chapter: Skills
% ------------------------

\chap{SKILLS}{ \\
Programming Languages: Bash, C, C++, Go, Java, Javascript, Python, Rust, SQL \\
Frameworks and Tools: Databricks, Django, FastAPI, Git, Github, Jira, LaTeX, Protobuf, React, Svelte, TeamDynamix
}
\end{document}
